---
title: "Number of Marriage Licenses Issued Over Time"
author: 
  - Michelle Ji
date: 19 September 2024
date-format: long
abstract: This paper details the number of marriage issued over time in Toronto. Based on the analysis, there seems a slight incfrease in the average marriage licenses issued, however the positive correlation between marriage license and time is not extremely strong. 
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

marriage_data <- read_csv("analysis_data.csv")
```


# Introduction
In this paper, we looked at the number of marriage licenses over time in Toronto, from City Of Toronto OpenData. We use @citeR and @rohan to complete our analysis. We used data from @rOpendatatoronto



# Data {#sec-data}

```
We can look at our figure about the marriage licenses issued over time in Toronto (@fig-marriage). 

```{r}
#| label: fig-marriage
#| fig-cap: Relationship between time and number of licenses issued
#| echo: false
#| warning: false
#| message: false
  
ggplot(marriage_data, aes(x = date, y = marriage_licenses)) + # Line plot
  geom_point(color = "red", size = 2) + # Add points for each date
  labs(
    title = "Marriage Licenses Issued Over Time",
    x = "Date",
    y = "Number of Marriage Licenses"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))
```





\newpage


# References


